### 2018-11-26 Sections/acknowledgements.tex
Dist quantum search update

\begin{itemize}
\item We acknowledge Gavin Brennen, Joseph Clark, Eric Cavalcanti, Charlotte Bridault, Marco Tomamichel, Ryan Mann, Jonathan Olson, Samuel Marks \& Alexis Shaw for helpful discussions.
\item We thank the authors of QCircuit (\href{http://physics.unm.edu/CQuIC/Qcircuit/}{http://physics.unm.edu/CQuIC/Qcircuit/}) for providing this very helpful package.
\item Peter P. Rohde is funded by an Australian Research Council Future Fellowship (project FT160100397).
\item Tim Byrnes is supported by the Shanghai Research Challenge Fund; New York University Global Seed Grants for Collaborative Research; National Natural Science Foundation of China (Grant No. 61571301); the Thousand Talents Program for Distinguished Young Scholars (Grant No. D1210036A); and the NSFC Research Fund for International Young Scientists (Grant No. 11650110425); NYU-ECNU Institute of Physics at NYU Shanghai; and the Science \& Technology Commission of Shanghai Municipality (Grant No. 17ZR1443600).
\item Jonathan P. Dowling would like to acknowledge support from the US Air Force Office of Scientific Research, the Army Research Office, the National Science Foundation, and the Northrop-Grumman Corporation.
\item We thank almost unethical quantities of 1,3,7-Trimethylxanthine\index{1,3,7-Trimethylxanthine}\index{Caffeine} for aiding in the motivation for this work.
\end{itemize}

>>>>

\begin{itemize}
\item We acknowledge Gavin Brennen, Chris Ferrie, Joseph Clark, Eric Cavalcanti, Charlotte Bridault, Marco Tomamichel, Ryan Mann, Jonathan Olson, Samuel Marks \& Alexis Shaw for helpful discussions.
\item We thank the authors of QCircuit (\href{http://physics.unm.edu/CQuIC/Qcircuit/}{http://physics.unm.edu/CQuIC/Qcircuit/}) for providing this very helpful package.
\item Peter P. Rohde is funded by an Australian Research Council Future Fellowship (project FT160100397).
\item Tim Byrnes is supported by the Shanghai Research Challenge Fund; New York University Global Seed Grants for Collaborative Research; National Natural Science Foundation of China (Grant No. 61571301); the Thousand Talents Program for Distinguished Young Scholars (Grant No. D1210036A); and the NSFC Research Fund for International Young Scientists (Grant No. 11650110425); NYU-ECNU Institute of Physics at NYU Shanghai; and the Science \& Technology Commission of Shanghai Municipality (Grant No. 17ZR1443600).
\item Jonathan P. Dowling would like to acknowledge support from the US Air Force Office of Scientific Research, the Army Research Office, the National Science Foundation, and the Northrop-Grumman Corporation.
\item We thank almost unethical quantities of 1,3,7-Trimethylxanthine\index{1,3,7-Trimethylxanthine}\index{Caffeine} for aiding in the motivation for this work.
\end{itemize}

### 2018-11-26 Sections/cloud_quantum_computing.tex
Dist quantum search update

To the contrary, unlike most quantum algorithms, whose power grows exponentially with the number of qubits (increasing returns\index{Increasing returns}), the distributed quantum search algorithm exhibits diminishing returns\index{Diminishing returns} with the degree of parallelisation -- the computational gain from adding one additional node to the network scales as,
\begin{align}
\sqrt{\frac{M+1}{M}},
\end{align}
which in the large $M$ limit goes to,
\begin{align}
\lim_{M\to\infty} \sqrt{\frac{M+1}{M}} = 1.
\end{align}
That is, increasing the number of nodes from 1 to 2 has far greater net gain than increasing them from 100 to 101. In fact, asymptotically, the gain from adding an additional node vanishes in the limit of a high degree of parallelisation.

>>>>

To the contrary, unlike most quantum algorithms, whose power grows exponentially with the number of qubits (increasing returns\index{Increasing returns}), the distributed quantum search algorithm exhibits diminishing returns\index{Diminishing returns} with the degree of parallelisation -- the computational gain from adding one additional node to the network scales as,
\begin{align}
G=\sqrt{\frac{M+1}{M}},
\end{align}
shown in Fig.~\ref{fig:dist_quant_search}, which in the large $M$ limit asymptotes to,
\begin{align}
\lim_{M\to\infty} \sqrt{\frac{M+1}{M}} = 1.
\end{align}
That is, increasing the number of nodes from 1 to 2 has far greater net gain than increasing them from 100 to 101. In fact, asymptotically, the gain from adding an additional node vanishes in the limit of a high degree of parallelisation.

\begin{figure}[!htpb]
	\includegraphics[clip=true, width=0.475\textwidth]{distributed_quantum_search}
	\captionspacefig \caption{Computational gain from adding a single extra node to a parallelised implementation of the quantum search algorithm.}\label{fig:dist_quant_search}
\end{figure}

For this reason, parallelised implementation of a quantum search is not an example of a distributed quantum computation which achieves exponential gain with the addition of new nodes (i.e qubits). Rather, for this specific application it's far more optimal to consolidate quantum resources into a single larger instance of a quantum search algorithm than using the quantum \textsc{MapReduce}\index{Quantum MapReduce} architecture to parallelise it.

### 2018-11-26 Sections/statement_of_contributions.tex
QFT complete
Dist quantum search update

\begin{itemize}
	\item Peter P. Rohde conceived, directed and edited this project, developed the original ideas, and prepared most of the manuscript.
	\item Zixin Huang prepared Secs.~\ref{sec:telescopy}, \ref{sec:CV_QC}, \ref{sec:essay_future_QKD}, \ref{sec:attacks_QKD}, \ref{sec:shallow_circs} \& \ref{sec:NISQ}.
	\item Heliang Huang \& Zuen Su prepared Part.~\ref{part:SotA}.
	\item Chris Ferrie \& Nana Liu prepared Sec.~\ref{sec:quantum_mind}.
	\item Simon Devitt prepared Secs.~\ref{???}.
	\item Rohit Ramakrishnan prepared Sec.~\ref{???}.
	\item Si-Hui Tan \& Atul Mantri contributed to Sec.~\ref{???}.
	\item Nana Liu prepared Sec.~\ref{sec:verification}.
	\item Scott Harrison prepared Secs.~\ref{sec:econ_prop}, \ref{sec:policy} \& \ref{sec:game_theory}.
	\item Darryl Vietch contributed to Sec.~\ref{???}.
	\item Chandrashekar Radhakrishnan prepared Sec.~\ref{sec:artificial_atoms}.
	\item Jonathan P. Dowling contributed to editing.
	\item Tim Byrnes \& Jonathan P. Dowling prepared Sec.~\ref{sec:quant_space_race}.
	\item William J. Munro prepared Sec.~\ref{sec:rep_net}. 
	\item All authors played active roles in the discussions that developed this work. 
\end{itemize}

>>>>

\begin{itemize}
	\item Peter P. Rohde conceived, directed and edited this project, developed the original ideas, and prepared most of the manuscript.
	\item Zixin Huang prepared Secs.~\ref{sec:telescopy}, \ref{sec:CV_QC}, \ref{sec:essay_future_QKD}, \ref{sec:attacks_QKD}, \ref{sec:shallow_circs} \& \ref{sec:NISQ}.
	\item Heliang Huang \& Zuen Su prepared Part.~\ref{part:SotA}.
	\item Simon Devitt prepared Secs.~\ref{???}.
	\item Rohit Ramakrishnan prepared Sec.~\ref{???}.
	\item Si-Hui Tan \& Atul Mantri contributed to Sec.~\ref{???}.
	\item Nana Liu prepared Secs.~\ref{sec:verification} \& \ref{sec:quantum_mind}.
	\item Scott Harrison prepared Secs.~\ref{sec:econ_prop}, \ref{sec:policy} \& \ref{sec:game_theory}.
	\item Darryl Vietch contributed to Sec.~\ref{???}.
	\item Chandrashekar Radhakrishnan prepared Secs.~\ref{sec:superconducting_qubits} \& \ref{sec:artificial_atoms}.
	\item Jonathan P. Dowling contributed to editing.
	\item Tim Byrnes \& Jonathan P. Dowling prepared Sec.~\ref{sec:quant_space_race}.
	\item William J. Munro prepared Sec.~\ref{sec:rep_net}. 
	\item All authors played active roles in the discussions that developed this work. 
\end{itemize}
